Capstone Movielens Report

### 2025-12-19 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the data visualization functions' descriptions.

:::
::: { #func.data.plot.args.line_col .sidebar }
  - **line_col:** (Character string, \textcolor{blue}{blue} by default) Line color.

@@

:::
::: { #func.data.plot.left.n.args.line_col .sidebar }
  - **line_col:** (Character string, \textcolor{red}{red} by default) Line color.

@@

:::
::: { #func.data.plot.left_detailed.args.line_col .sidebar }
  - **line_col1** (Character string, \textcolor{blue}{blue} by default) The line color (main graqh).

:::
::: { #func.data.plot.left_detailed.args.line_col .sidebar }
  - **line_col2** (Character string, \textcolor{red}{red} by default) The line color (second graph: the left part of the main graph, which is shown on an enlarged scale).

>>>>

:::
::: { #func.data.plot.args.line_col .sidebar }
  - **line_col:** (Character string, ***\textcolor{blue}{blue}*** by default) Line color.

@@

:::
::: { #func.data.plot.left.n.args.line_col .sidebar }
  - **line_col:** (Character string, ***\textcolor{red}{red}*** by default) Line color.

@@

:::
::: { #func.data.plot.left_detailed.args.line_col .sidebar }
  - **line_col1** (Character string, ***\textcolor{blue}{blue}*** by default) The line color (main graqh).

:::
::: { #func.data.plot.left_detailed.args.line_col .sidebar }
  - **line_col2** (Character string, ***\textcolor{red}{red}*** by default) The line color (second graph: the left part of the main graph, which is shown on an enlarged scale).
